Cognate Priming: Report

### 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
Render report with figures

ggplot(m, aes(time_bin_center, .value)) +
	facet_wrap(~fct_rev(lp)) +
	geom_hline(yintercept = 0.5) +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.15, size = 0.75) +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1.25) +
	stat_summary(data = gaze_relaxed, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
							   colour = trial_type),
				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
				 position = position_dodge(width = 0.3)) +
	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 1, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_x_continuous(breaks = min(gaze_relaxed$time_bin_center):max(gaze_relaxed$time_bin_center), labels = unique(gaze_relaxed$time_bin)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 9)
	)
```

>>>>

ggplot(m, aes(time_bin_center, .value)) +
	facet_wrap(~fct_rev(lp)) +
	geom_hline(yintercept = 0.5, colour = "white") +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.15, size = 0.65) +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1.25) +
	stat_summary(data = gaze_relaxed, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
										  colour = trial_type),
				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
				 position = position_dodge(width = 0.3)) +
	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 1, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_x_continuous(breaks = min(gaze_relaxed$time_bin_center):max(gaze_relaxed$time_bin_center), labels = unique(gaze_relaxed$time_bin)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 9),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank()
	)
```
